Quantum parallel Markov chain Monte Carlo

### 2021-11-03 main.tex
ready for grover

In the presence of these trade-offs,

>>>>

\emph{In the presence of these trade-offs, we seek to enjoy the benefits of parallel MCMC while (\textcolor{red}{a}) limiting the total amount of computing necessary and (\textcolor{red}{b})  retaining parallel computing resources for computational bottlenecks such as proposal generations and target evaluations.}

GROVER
